Postural developments modulate children's visual access to social information

### 2018-07-17 writeup-cogsci/cogsci2018_remakePlots.Rmd
script to remake a few plots

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, message=F, sanitize = T)
```

@@

ggarrange(p1,p2)
```
## Changes in Posture and Orientation
The proportion of time infants spent sitting decreased with age, and the proportion of time infants spent standing increased with age. Both 8-month-olds and 12-month-olds spent equivalent amounts of time lying/crawling, which was markedly decreased in the 16-month-olds, who spent most of their time sitting or standing (see Figure \ref{fig:posture}).  We also observed changes in children's orientation relative to their caregivers: the 8-month-olds spent more time with their caregiver behind them supporting their sitting positions (see Figure \ref{fig:posture}).

@@

ggplot(detectionsByAge, aes(x = age.at.test, y = detections, color = detectorType, size=len.min)) +
  geom_jitter(width = .25) +
  geom_smooth(size=1) +
  scale_x_continuous(breaks=c(8,12,16)) +
  scale_size_continuous(range=c(.01,2),name = "Video Length (mins)") +
  labs(y = "Prop. detected", x = element_blank()) +
  theme_few() + 
  theme(legend.position="none") +
  facet_grid(~detectorType) 
```

@@

ggarrange(p1, p2)

@@

ggarrange(p1,p2, p3, p4)
```

>>>>

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, message=F, sanitize = T, dev = "cairo_pdf")
```

@@

ggarrange(p1,p2)
fig1=ggarrange(p1,p2)
ggsave("Fig3-TimebyPos.png", width = 5, height = 5,unit =  "in", plot = fig1, path="./figs/", device = "png",dpi = 300)
```
## Changes in Posture and Orientation
The proportion of time infants spent sitting decreased with age, and the proportion of time infants spent standing increased with age. Both 8-month-olds and 12-month-olds spent equivalent amounts of time lying/crawling, which was markedly decreased in the 16-month-olds, who spent most of their time sitting or standing (see Figure \ref{fig:posture}).  We also observed changes in children's orientation relative to their caregivers: the 8-month-olds spent more time with their caregiver behind them supporting their sitting positions (see Figure \ref{fig:posture}).

@@

fig4=ggplot(detectionsByAge, aes(x = age.at.test, y = detections, color = detectorType, size=len.min)) +
  geom_jitter(width = .25) +
  geom_smooth(size=1) +
  scale_x_continuous(breaks=c(8,12,16)) +
  scale_size_continuous(range=c(.01,2),name = "Video Length (mins)") +
  labs(y = "Prop. detected", x = element_blank()) +
  theme_few() + 
  theme(legend.position="none") +
  facet_grid(~detectorType)

ggsave("Fig4-DetbyAge.png", width = 5, height = 4,unit =  "in", plot = fig4, path="./figs/", device = "png",dpi = 300)
```

@@

ggarrange(p1, p2)
fig5=ggarrange(p1, p2)
ggsave("Fig5-DetbyOrientation.png", width = 6, height = 3,unit =  "in", plot = fig5, path="./figs/", device = "png",dpi = 300)

@@

fig7=ggarrange(p1,p2, p3, p4)

ggsave("Fig7-Naming.png", width = 3, height = 3,unit =  "in", plot = fig7, path="./figs/", device = "png",dpi = 300)
```
